### 2021-09-14 paper/localpsf.tex
simplify Poisson weighting function discussion

We choose the weighting functions, $w_i$, to be the solutions to the following optimization problems:
\begin{equation}
	\label{eq:wi_optimization_problem_intro}
	\begin{aligned}
		\min_{w_i \in H^2_N(\Omega)} &\quad \frac{1}{2}\norm{\Delta w_i}_{L^2(\Omega)}^2 \\
		\text{such that} &\quad w_i(x_j) = \delta_{ij}, \quad j=1,\dots,q.
	\end{aligned}
\end{equation}
Here $\Delta$ is the Laplacian on $\Omega$, $H^2_N(\Omega)$ is the space of all functions in the Sobolev space $H^2(\Omega)$ with Neumann zero boundary conditions, and the right hand side of the constraint, $\delta_{ij}$, is the Kronecker delta, which takes value one if $i=j$ and zero if $i \neq j$. Since the Laplacian measures local deviation from flatness \cite{JACOBSEN}, the function $w_i$ is the flattest function, in a least-squares sense, that takes the value one at the sample point $x_i$, and the value zero at the other sample points $x_j$, $i \neq j$. Computing the weighting functions $w_i$ requires solving two Poisson PDEs per weighting function, and these PDEs are solved cheaply using multigrid. We call this interpolation scheme \emph{Poisson interpolation}. The advantage of Poisson interpolation over other interpolation methods, most notably radial basis function interpolation \cite{ESCANDE}, is that Poisson interpolation incorporates information about the domain geometry when constructing the weighting functions. This is illustrated in Figure FIG.

@@

Consider the following optimization problem,
\begin{equation}
	\label{eq:wi_optimization_problem_generic}
	\begin{aligned}
	\min_{v \in H^2_N(\Omega)} &\quad \frac{1}{2}\norm{\Delta v}_{L^2(\Omega)}^2 \\
	\text{such that} &\quad v(x_j) = \interpolatedvalues_j, \quad j=1,\dots,\convrank,
	\end{aligned}
\end{equation}
in which one seeks a smooth function $v$ that takes the values $\interpolatedvalues_j \in \mathbb{R}$ at the points $x_j$. Here $\Delta$ is the Laplacian on $\Omega$ and $H^2_N(\Omega)$ is the space of all functions in $H^2(\Omega)$ with Neumann zero boundary conditions. We choose the $i^\text{th}$ weighting function, $w_i(x)$, to be the solution to optimization problem \eqref{eq:wi_optimization_problem_generic}, with 
\begin{equation*}
	b_j = w_i(x_j) = 
	\begin{cases}
		1, & j=i\\
		0, & j \neq i.
	\end{cases}
\end{equation*}
Using these weighting functions yields the ``flattest possible'' interpolation of the convolution kernels $\convkernel_i$, in a least-squares sense (Theorem \ref{thm:smoothest_interpolant}). Also, these weighting functions sum to one pointwise (Proposition \ref{thm:wi_sum_to_one}).

%For each $i=1,\dots,\convrank$, optimization problem \eqref{eq:wi_optimization_problem} is an example of the following generic optimization problem:
%\begin{equation}
%	\label{eq:wi_optimization_problem_generic}
%	\begin{aligned}
%		\min_{v \in H^2_N(\Omega)} &\quad \frac{1}{2}\norm{\Delta v}_{L^2(\Omega)}^2 \\
%		\text{such that} &\quad v(x_j) = \interpolatedvalues_j, \quad j=1,\dots,\convrank,
%	\end{aligned}
%\end{equation}
%where $\interpolatedvalues_j \in \mathbb{R}$, $j=1,\dots,\convrank$ are given function values that $v$ must take at the points $x_j$.

We may efficiently solve optimization problem \eqref{eq:wi_optimization_problem_generic} via the following procedure:
\begin{enumerate}
	\item For each sample point $x_i$, we compute a function $\firstgreens_i$ by solving the following Neumann Poisson problem:
	\begin{equation}
		\label{eq:psi_eq}
		\begin{cases}
			\Delta \firstgreens_i = \delta_{x_i} - 1/|\Omega|, & \text{in }\Omega, \\
			\nu \cdot \nabla \firstgreens_i = 0 & \text{on } \partial \Omega,
		\end{cases}
	\end{equation}
	with condition $\int_\Omega \firstgreens_i(x) dx = 0$. Here $\delta_{x_i}$ is the point source centered at $x_i$, $|\Omega|$ is the measure of the domain $\Omega$, and $\nu$ is the normal vector to $\partial \Omega$.
	\item For each function $\firstgreens_i$, we compute a function $\secondgreens_i$ by solving another Neumann Poisson problem:
	\begin{equation}
		\label{eq:theta_eq}
		\begin{cases}
			\Delta \secondgreens_i = \firstgreens_i, & \text{in }\Omega, \\
			\nu \cdot \nabla \secondgreens_i = 0 & \text{on } \partial \Omega,
		\end{cases}
	\end{equation}
	with condition $\int_\Omega \secondgreens_i(x) dx = 0$.
	\item The solution to optimization problem \eqref{eq:wi_optimization_problem_generic}, which we denote by $v_*$, is formed as follows:
	\begin{equation}
		\label{eq:optimal_v}
		v_*(x) := \beta + \sum_{i=1}^\convrank c_i \secondgreens_i(x),
	\end{equation}
	where the constants $c_i \in \mathbb{R}$, $i=1,\dots,\convrank$, and $\beta \in \mathbb{R}$ are the solution to the following linear system:
	\begin{equation}
		\label{eq:interpolation_linear_system}
		\begin{bmatrix}
			\pointinteractionmatrix & \mathbf{1} \\ \mathbf{1}^T & 0
		\end{bmatrix}
		\begin{bmatrix}
			\mathbf{c} \\ \beta
		\end{bmatrix}
		=
		\begin{bmatrix}
			\mathbf{\interpolatedvalues} \\ 0
		\end{bmatrix}.
	\end{equation}
	Here $\mathbf{c} \in \mathbb{R}^\convrank$ is the vector with $i$th component $c_i$, $\mathbf{1} \in \mathbf{R}^\convrank$ is the column vector of all ones, $\mathbf{\interpolatedvalues} \in \mathbb{R}^\convrank$ is the vector with $i$th component $\interpolatedvalues_i$, and $\pointinteractionmatrix \in \mathbb{R}^{\convrank \times \convrank}$ is the matrix with entries given by
	\begin{equation}
		\label{eq:S_matrix}
		\pointinteractionmatrix_{ij} := \left( \firstgreens_i, \firstgreens_j \right)_{L^2(\Omega)}.
	\end{equation}
\end{enumerate}
In Theorem \ref{thm:wi_no_breakdown}, we prove that this procedure does not break down, so long as there is no repetition in the points $x_i$. Linear system \eqref{eq:interpolation_linear_system} is the KKT system that arises if one solves optimization problem \eqref{eq:wi_optimization_problem_generic} on the $\convrank+1$-dimensional subspace spanned by the functions $\firstgreens_i$, $i=1,\dots,\convrank$, and the constant function $C(x)=1$, rather than solving the optimization problem on the infinite dimensional space $H^2_N(\Omega)$. In Theorem \ref{thm:wi_alg_is_correct}, we prove that the function $v_*$ produced by this process solves optimization problem \eqref{eq:wi_optimization_problem_generic} on $H^2_N(\Omega)$.

>>>>

%We choose the weighting functions, $w_i$, to be the solutions to the following optimization problems:
%\begin{equation}
%	\label{eq:wi_optimization_problem_intro}
%	\begin{aligned}
%		\min_{w_i \in H^2_N(\Omega)} &\quad \frac{1}{2}\norm{\Delta w_i}_{L^2(\Omega)}^2 \\
%		\text{such that} &\quad w_i(x_j) = \delta_{ij}, \quad j=1,\dots,q.
%	\end{aligned}
%\end{equation}
%Here $\Delta$ is the Laplacian on $\Omega$, $H^2_N(\Omega)$ is the space of all functions in the Sobolev space $H^2(\Omega)$ with Neumann zero boundary conditions, and the right hand side of the constraint, $\delta_{ij}$, is the Kronecker delta, which takes value one if $i=j$ and zero if $i \neq j$. Since the Laplacian measures local deviation from flatness \cite{JACOBSEN},

We choose the $i$th weighting function, $w_i$, to be the flattest function, in a least-squares sense, that takes the value one at the sample point $x_i$, and the value zero at the other sample points $x_j$, $i \neq j$. Computing the weighting functions $w_i$ requires solving two Poisson PDEs per weighting function, and these PDEs are solved cheaply using multigrid. We call this interpolation scheme \emph{Poisson interpolation}. The advantage of Poisson interpolation over other interpolation methods, most notably radial basis function interpolation \cite{ESCANDE}, is that Poisson interpolation incorporates information about the domain geometry when constructing the weighting functions. This is illustrated in Figure FIG.

@@

Consider the following optimization problem,
\begin{equation}
	\label{eq:wi_optimization_problem_generic}
	\begin{aligned}
	\min_{v \in H^2_N(\Omega)} &\quad \frac{1}{2}\norm{\Delta v}_{L^2(\Omega)}^2 \\
	\text{such that} &\quad v(x_j) = \interpolatedvalues_j, \quad j=1,\dots,\convrank,
	\end{aligned}
\end{equation}
in which one seeks a smooth function $v$ that takes the values $\interpolatedvalues_j \in \mathbb{R}$ at the points $x_j$. Here $\Delta$ is the Laplacian on $\Omega$ and $H^2_N(\Omega)$ is the space of all functions in $H^2(\Omega)$ with Neumann zero boundary conditions. We choose the $i^\text{th}$ weighting function, $w_i(x)$, to be the solution to optimization problem \eqref{eq:wi_optimization_problem_generic}, with 
\begin{equation*}
	b_j = w_i(x_j) = 
	\begin{cases}
		1, & j=i\\
		0, & j \neq i.
	\end{cases}
\end{equation*}
In Theorem \ref{thm:smoothest_interpolant}, we show that using these weighting functions yields the ``flattest possible'' \cite{JACOBSEN} interpolation of the convolution kernels, $\convkernel_i$, in a least-squares sense. Also, these weighting functions sum to one pointwise (Proposition \ref{thm:wi_sum_to_one}).

We may efficiently solve optimization problem \eqref{eq:wi_optimization_problem_generic} via the following procedure:
\begin{enumerate}
	\item For each sample point $x_i$, we compute a function $\firstgreens_i$ by solving the following Neumann Poisson problem:
	\begin{equation}
		\label{eq:psi_eq}
		\begin{cases}
			\Delta \firstgreens_i = \delta_{x_i} - 1/|\Omega|, & \text{in }\Omega, \\
			\nu \cdot \nabla \firstgreens_i = 0 & \text{on } \partial \Omega,
		\end{cases}
	\end{equation}
	with condition $\int_\Omega \firstgreens_i(x) dx = 0$. Here $\delta_{x_i}$ is the point source centered at $x_i$, $|\Omega|$ is the measure of the domain $\Omega$, and $\nu$ is the normal vector to $\partial \Omega$.
	\item For each function $\firstgreens_i$, we compute a function $\secondgreens_i$ by solving another Neumann Poisson problem:
	\begin{equation}
		\label{eq:theta_eq}
		\begin{cases}
			\Delta \secondgreens_i = \firstgreens_i, & \text{in }\Omega, \\
			\nu \cdot \nabla \secondgreens_i = 0 & \text{on } \partial \Omega,
		\end{cases}
	\end{equation}
	with condition $\int_\Omega \secondgreens_i(x) dx = 0$.
	\item The solution to optimization problem \eqref{eq:wi_optimization_problem_generic}, which we denote by $v_*$, is formed as follows:
	\begin{equation}
		\label{eq:optimal_v}
		v_*(x) := \beta + \sum_{i=1}^\convrank c_i \secondgreens_i(x),
	\end{equation}
	where the constants $c_i \in \mathbb{R}$, $i=1,\dots,\convrank$, and $\beta \in \mathbb{R}$ are the solution to the following linear system:
	\begin{equation}
		\label{eq:interpolation_linear_system}
		\begin{bmatrix}
			\pointinteractionmatrix & \mathbf{1} \\ \mathbf{1}^T & 0
		\end{bmatrix}
		\begin{bmatrix}
			\mathbf{c} \\ \beta
		\end{bmatrix}
		=
		\begin{bmatrix}
			\mathbf{\interpolatedvalues} \\ 0
		\end{bmatrix}.
	\end{equation}
	Here $\mathbf{c} \in \mathbb{R}^\convrank$ is the vector with $i$th component $c_i$, $\mathbf{1} \in \mathbf{R}^\convrank$ is the column vector of all ones, $\mathbf{\interpolatedvalues} \in \mathbb{R}^\convrank$ is the vector with $i$th component $\interpolatedvalues_i$, and $\pointinteractionmatrix \in \mathbb{R}^{\convrank \times \convrank}$ is the matrix with entries given by
	\begin{equation}
		\label{eq:S_matrix}
		\pointinteractionmatrix_{ij} := \left( \firstgreens_i, \firstgreens_j \right)_{L^2(\Omega)}.
	\end{equation}
\end{enumerate}
Linear system \eqref{eq:interpolation_linear_system} is the KKT system that arises if one solves optimization problem \eqref{eq:wi_optimization_problem_generic} on the $\convrank+1$-dimensional subspace of $H^2_N(\Omega)$ spanned by the functions $\secondgreens_i$, $i=1,\dots,\convrank$, and the constant function $C(x)=1$. In Theorem \ref{thm:wi_no_breakdown}, we prove that this procedure does not break down, and in Theorem \ref{thm:wi_alg_is_correct}, we prove that the function $v_*$ produced by this procedure is the solution to optimization problem \eqref{eq:wi_optimization_problem_generic} on $H^2_N(\Omega)$.
